### 2025-01-09 paper/icml25/first/sects/related.tex
more on related work for MARL

\paragraph{Multi-Agent Reinforcement Learning}
Multi-Agent Reinforcement Learning (MARL) is a subfield of reinforcement learning that focuses on learning policies for multiple agents that interact with each other. 
This field has a wide range of applications, 
including robotics, 
traffic control, 
and game playing, 
and involves different types of agents such as cooperative, competitive, and mixed. 
In this paper, we primarily focus on cooperative multi-agent scenarios, 
where agents need to collaborate to achieve a common goal. 
Prominent works in this area include extensions of single-agent algorithms to multi-agent settings, 
such as MADDPG~\cite{DBLP:conf/nips/LoweWTHAM17} and MAPPO~\cite{DBLP:conf/nips/YuVVGWBW22}, 
as well as novel solutions to unique challenges in multi-agent settings. Examples of these solutions are COMA~\cite{DBLP:conf/aaai/FoersterFANW18} for multi-agent credit assignment, 
QMIX~\cite{DBLP:conf/icml/RashidSWFFW18} for coordination in cooperative multi-agent settings, 
and Mean Field MARL~\cite{DBLP:conf/icml/YangLLZZW18} for handling a large number of agents.

>>>>

\paragraph{Multi-Agent Reinforcement Learning}
Multi-Agent Reinforcement Learning (MARL) is a subfield of reinforcement learning that focuses on learning policies for multiple agents that interact with each other~\cite{albrecht2024multi}. 
This field has a wide range of applications, 
including robotics~\cite{DBLP:journals/air/ChungFYN24}, 
traffic control~\cite{DBLP:journals/tits/ChuWCL20}, 
and game playing~\cite{DBLP:conf/iclr/BakerKMWPMM20,jaderberg2019human}, 
and involves different types of agents such as cooperative~\cite{DBLP:journals/corr/abs-2312-05162}, competitive, and mixed. 
In this paper, we primarily focus on cooperative multi-agent scenarios, 
where agents need to collaborate to achieve a common goal. 
Prominent works in this area include extensions of single-agent algorithms to multi-agent settings, 
such as MADDPG~\cite{DBLP:conf/nips/LoweWTHAM17} and MAPPO~\cite{DBLP:conf/nips/YuVVGWBW22}, 
as well as novel solutions to unique challenges in multi-agent settings. Examples of these solutions are COMA~\cite{DBLP:conf/aaai/FoersterFANW18} for multi-agent credit assignment, 
QMIX~\cite{DBLP:conf/icml/RashidSWFFW18} for coordination in cooperative multi-agent settings, 
and Mean Field MARL~\cite{DBLP:conf/icml/YangLLZZW18} for handling a large number of agents.
